\textbf{Too Beautiful to be Fake: Attractive Faces are Less Likely to be Judged as Artificially Generated}

### 2022-09-13 analysis.Rmd
ms

plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size = 3) {
  # library(emojifont)
  ggwaffle::waffle_iron(dfsub, what, rows = rows) |>
    # mutate(label = emojifont::fontawesome('fa-smiley')) |>
    # mutate(label = emojifont::emoji('smiley')) |>
    ggplot(aes(x, y)) +
    geom_point(aes(color = group), shape = "square", size = size) +
    # ggwaffle::geom_waffle(color = "white") +
    # geom_point() +
    # geom_text(aes(color=group ,label=label), family='fontawesome-webfont', size=4) +
    # geom_text(aes(color=group ,label=label), family='EmojiOne', size=4) +
    coord_equal() +
    ggtitle(title) +
    labs(fill = "", color = "") +
    # scale_x_continuous(expand = c(0, 0)) +
    # scale_y_continuous(expand = c(0, 0)) +
    theme_void() +
    # ggwaffle::theme_waffle() +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}
```

```{r fig.width=20, fig.height=15}
p1 <- estimate_density(dfsub$Age) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(fill = "#FF9800")

@@

p5 <- dfsub |>
  group_by(Nationality) |>
  mutate(n = n()) |>
  ungroup() |>
  mutate(Nationality = fct_reorder(Nationality, desc(n))) |>
  ggplot(aes(Nationality)) +
  geom_bar(aes(fill = Nationality)) +
  scale_fill_viridis_d(guide = "none") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

patchwork::wrap_plots(list(p1, p2, p3, p4, p5, p6, p8))
```

@@

```{r message=FALSE, warning=FALSE}
dats |>
  ggplot(aes(x = Score, y = Predicted)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  # geom_ribbon(data = preds, aes(ymin = CI_low, ymax = CI_high, group = Stimulus_SameSex), alpha = 0.3) +
  geom_line(data = preds, aes(color = Sex, linetype = Stimulus_Interest)) +
  scale_fill_gradientn(colors = c("white", "#FF9800", "#F44336"), guide = "none") +
  scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
  scale_linetype_manual(values = c("TRUE" = "solid", "FALSE" = "dashed")) +
  scale_x_continuous(expand = c(0, 0), labels = scales::percent()) +
  scale_y_continuous(expand = c(0, 0), labels = scales::percent()) +
  facet_grid(y ~ x, switch = "both") +
  theme_modern() +
  labs(title = "Collinearity in the Stimuli Ratings") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggnewscale::new_scale_fill() +
  scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
  ggside::geom_xsidedensity(aes(fill = Sex), color = NA, alpha = 0.3) +
  ggside::geom_ysidedensity(aes(fill = Sex), color = NA, alpha = 0.3) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all")
```

@@

  # Plot
  p <- df |>
    ggplot(aes_string(x = var, y = "Real")) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
    scale_fill_gradientn(colors = c("white", fill), guide = "none") +
    ggnewscale::new_scale_fill() +
    geom_hline(yintercept = 0.5, linetype = "dotted") +
    # geom_point2(alpha = 0.25, size = 4, color = "black") +
    geom_line(data = y_conf, aes(y = Predicted, group = interaction(Belief, Sex), color = Sex), linetype = "dashed") +
    geom_ribbon(data = y_real, aes(y = Predicted, group = Sex, fill = Sex, ymin = CI_low, ymax = CI_high), alpha = 1 / 3) +
    geom_line(data = y_real, aes(y = Predicted, color = Sex), size=1) +
    # geom_ribbon(data = trend, aes(y = Predicted, group=Sex, fill=Sex, ymin = CI_low, ymax = CI_high), alpha = 1/6) +
    # geom_line(data = trend, aes(y = Predicted, color=Sex, linetype=Trend, group=interaction(Sex, group)), size=0.6) +
    geom_text(data = sig, aes(y = y, x = x, label = label, color = Sex), size = 8) +
    scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
    scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
    guides(fill = guide_legend(override.aes = list(alpha = 1))) +
    theme_modern(axis.title.space = 5) +
    ggside::geom_xsidedensity(fill = fill, color = "white") +
    ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
    ggside::theme_ggside_void() +
    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
    ggside::scale_xsidey_continuous(expand = c(0, 0))

@@

```{r message=FALSE, warning=FALSE}
rez_at <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Attractive, 2) + (1|Participant) + (1|Stimulus)",
  var = "Attractive", fill = "#F44336"
)
rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Beauty, 2) + Trustworthy + (1|Participant) + (1|Stimulus)",
  var = "Beauty", fill = "#E91E63"
)
rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Trustworthy, 2) + Beauty + (1|Participant) + (1|Stimulus)",
  var = "Trustworthy", fill = "#4CAF50"
)
rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Familiar, 2) + (1|Participant) + (1|Stimulus)",
  var = "Familiar", fill = "#2196F3"
)

(rez_at$p +
  theme(axis.text.x = element_blank()) +
  labs(x = "Attractiveness") |
  rez_gl$p +
    labs(x = "Beauty") +
    theme(
      axis.text.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_blank()
    )
) /
  (rez_tr$p +
    labs(x = "Trustworthiness") |
    rez_fa$p +
      labs(x = "Familiarity") +
      theme(
        axis.text.y = element_blank(),
        axis.title.y = element_blank()
      )
  ) +
  plot_annotation(title = "Determinants of Reality Beliefs", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5))) +
  plot_layout(guides = "collect")
```

@@

## Interaction

@@

```{r message=FALSE, warning=FALSE}
model <- glmmTMB::glmmTMB(Belief ~ 1 + (1 | Participant) + (1 | Stimulus), data = df, family = "binomial")
dfsub <- modelbased::estimate_grouplevel(model) |>
  filter(Group == "Participant") |>
  transmute(Participant = Level, Simulation_Monitoring = Coefficient) |>
  merge(dfsub, by = "Participant")

model <- glmmTMB::glmmTMB(Belief_Confidence ~ Belief + (Belief | Participant) + (1 | Stimulus), data = df, family = glmmTMB::beta_family())
dfsub <- modelbased::estimate_grouplevel(model) |>
  filter(Group == "Participant") |>
  transmute(Participant = Level, Parameter, Coefficient) |>
  pivot_wider(names_from = "Parameter", values_from = "Coefficient") |>
  transmute(Participant, Confidence_Real_Model = BeliefReal, Confidence_Fake_Model = `(Intercept)`) |>
  merge(dfsub, by = "Participant")
```
```{r message=FALSE, warning=FALSE}
correlation::correlation(
  dfsub[c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model")],
  dfsub[c("Confidence_Fake", "Confidence_Real", "n_Real")],
)
```

@@

plot_correlation <- function(dfsub, x = "Confidence_Real", y = "IPIP6_Openness", xlab = x, ylab = y, fill = "grey") {
  param <- cor_test(dfsub, x, y, bayesian = TRUE)

@@

  # Plot
  dfsub |>
    ggplot(aes_string(x = x, y = y)) +
    geom_point2(
      size = 3,
      color = fill,
      # color = DVs[x],
      alpha = 2 / 3
    ) +
    geom_smooth(method = "lm", color = "black", formula = "y ~ x", alpha = 0.3) +
    labs(y = ylab, x = xlab) +
    geom_label(data = label, aes(x = x, y = y), label = str2expression(label$label), hjust = 0, vjust = 1) +
    theme_modern() +
    ggside::geom_xsidedensity(fill = "grey", color = "white") +
    ggside::geom_ysidedensity(fill = fill, color = "white") +
    ggside::theme_ggside_void() +
    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
    ggside::scale_xsidey_continuous(expand = c(0, 0))
}
```
```{r message=FALSE, warning=FALSE}
sr <- c("Simulation_Monitoring", "Confidence_Fake_Model", "Confidence_Real_Model", "Confidence_Fake", "Confidence_Real", "n_Real")

r <- make_correlation(dfsub[sr], select(dfsub, starts_with("IPIP")))
filter(r, BF > 1)

plot_correlation(dfsub,
  x = "Confidence_Real",
  y = "IPIP6_HonestyHumility",
  xlab = "Confidence_Real",
  ylab = "IPIP6_HonestyHumility",
  fill = "grey"
)
```

@@

>>>>

plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 10, size = 4) {
  # library(emojifont)
  ggwaffle::waffle_iron(dfsub, what, rows = rows) |>
    # mutate(label = emojifont::fontawesome('fa-smiley')) |>
    # mutate(label = emojifont::emoji('smiley')) |>
    ggplot(aes(x, y)) +
    geom_point(aes(color = group), shape = "square", size = size) +
    # ggwaffle::geom_waffle(color = "white") +
    # geom_point() +
    # geom_text(aes(color=group ,label=label), family='fontawesome-webfont', size=4) +
    # geom_text(aes(color=group ,label=label), family='EmojiOne', size=4) +
    coord_equal() +
    ggtitle(title) +
    labs(fill = "", color = "") +
    # scale_x_continuous(expand = c(0, 0)) +
    # scale_y_continuous(expand = c(0, 0)) +
    theme_void() +
    # ggwaffle::theme_waffle() +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}
```

```{r fig.width=20, fig.height=15}
p1 <- estimate_density(dfsub$Age) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(fill = "#FF9800") +
  labs(x = "Age", y = "") +
  theme_modern()

@@

p5 <- dfsub |>
  group_by(Nationality) |>
  mutate(n = n()) |>
  ungroup() |>
  mutate(Nationality = fct_reorder(Nationality, desc(n))) |>
  ggplot(aes(Nationality)) +
  geom_bar(aes(fill = Nationality)) +
  scale_fill_viridis_d(guide = "none") + 
  theme_modern() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

patchwork::wrap_plots(list(p1, p2, p3, p5, p4, p6))
```

@@

```{r message=FALSE, warning=FALSE}
dats |>
  ggplot(aes(x = Score, y = Predicted)) +
  stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
  # geom_ribbon(data = preds, aes(ymin = CI_low, ymax = CI_high, group = Stimulus_SameSex), alpha = 0.3) +
  geom_line(data = preds, aes(color = Sex, linetype = Stimulus_Interest)) +
  scale_fill_gradientn(colors = c("white", "#FF9800", "#F44336"), guide = "none") +
  scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
  scale_linetype_manual(values = c("TRUE" = "solid", "FALSE" = "dashed")) +
  scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
  scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
  facet_grid(y ~ x, switch = "both") +
  theme_modern() +
  labs(title = "Collinearity in the Stimuli Ratings") +
  theme(
    aspect.ratio = 1,
    strip.background = element_blank(),
    strip.placement = "outside",
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  ) +
  ggnewscale::new_scale_fill() +
  scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
  ggside::geom_xsidedensity(aes(fill = Sex), color = NA, alpha = 0.3) +
  ggside::geom_ysidedensity(aes(fill = Sex), color = NA, alpha = 0.3) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  ggside::ggside(collapse = "all")
```

@@

  # Plot
  p <- df |>
    ggplot(aes_string(x = var, y = "Real")) +
    stat_density_2d(aes(fill = ..density..), geom = "raster", contour = FALSE) +
    scale_fill_gradientn(colors = c("white", fill), guide = "none") +
    ggnewscale::new_scale_fill() +
    geom_hline(yintercept = 0.5, linetype = "dotted") +
    # geom_point2(alpha = 0.25, size = 4, color = "black") +
    geom_line(data = y_conf, aes(y = Predicted, group = interaction(Belief, Sex), color = Sex), linetype = "dashed") +
    geom_ribbon(data = y_real, aes(y = Predicted, group = Sex, fill = Sex, ymin = CI_low, ymax = CI_high), alpha = 1 / 3) +
    geom_line(data = y_real, aes(y = Predicted, color = Sex), size=1) +
    # geom_ribbon(data = trend, aes(y = Predicted, group=Sex, fill=Sex, ymin = CI_low, ymax = CI_high), alpha = 1/6) +
    # geom_line(data = trend, aes(y = Predicted, color=Sex, linetype=Trend, group=interaction(Sex, group)), size=0.6) +
    geom_text(data = sig, aes(y = y, x = x, label = label, color = Sex), size = 8) +
    scale_color_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_fill_manual(values = c("Male" = "#2196F3", "Female" = "#E91E63")) +
    scale_x_continuous(expand = c(0, 0), labels = scales::percent) +
    scale_y_continuous(expand = c(0, 0), breaks = c(0, 0.25, 0.5, 0.75, 1), labels = c("Fake", "25%", "50%", "75%", "Real")) +
    labs(y = "Simulation Monitoring") +
    guides(fill = guide_legend(override.aes = list(alpha = 1))) +
    theme_modern(axis.title.space = 5) +
    ggside::geom_xsidedensity(fill = fill, color = "white") +
    ggside::geom_ysidedensity(fill = "#9C27B0", color = "white") +
    ggside::theme_ggside_void() +
    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
    ggside::scale_xsidey_continuous(expand = c(0, 0))

@@

```{r message=FALSE, warning=FALSE, fig.width=fig.width, fig.height=fig.width}
rez_at <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Attractive, 2) + (1|Participant) + (1|Stimulus)",
  var = "Attractive", fill = "#F44336"
)
rez_gl <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Beauty, 2) + Trustworthy + (1|Participant) + (1|Stimulus)",
  var = "Beauty", fill = "#E91E63"
)
rez_tr <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Trustworthy, 2) + Beauty + (1|Participant) + (1|Stimulus)",
  var = "Trustworthy", fill = "#4CAF50"
)
rez_fa <- make_model(filter(df, Stimulus_Interest == TRUE),
  formula = "Sex / poly(Familiar, 2) + (1|Participant) + (1|Stimulus)",
  var = "Familiar", fill = "#2196F3"
)

fig1a <- (rez_at$p +
  theme(axis.text.x = element_blank()) +
  labs(x = "Attractiveness") |
  rez_gl$p +
    labs(x = "Beauty") +
    theme(
      axis.text.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_blank()
    )
) /
  (rez_tr$p +
    labs(x = "Trustworthiness") |
    rez_fa$p +
      labs(x = "Familiarity") +
      theme(
        axis.text.y = element_blank(),
        axis.title.y = element_blank()
      )
  ) +
  plot_annotation(title = "Determinants of Reality Beliefs", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5))) +
  plot_layout(guides = "collect") &
  theme(legend.position='top', legend.title = element_blank())
fig1a
```

@@

## Interaction with Self-Attractiveness

@@

@@

plot_correlation <- function(dfsub, x = "Confidence_Real", y = "IPIP6_Openness", xlab = x, ylab = y, fill = "grey", fillx = "purple") {
  param <- cor_test(dfsub, x, y, bayesian = TRUE)

@@

  # Plot
  dfsub |>
    ggplot(aes_string(x = x, y = y)) +
    geom_point2(
      size = 3,
      color = fillx,
      # color = DVs[x],
      alpha = 2 / 3
    ) +
    geom_smooth(method = "lm", color = "black", formula = "y ~ x", alpha = 0.3) +
    labs(y = ylab, x = xlab) +
    geom_label(data = label, aes(x = x, y = y), label = str2expression(label$label), hjust = 0, vjust = 1, size=rel(3.5)) +
    theme_modern(axis.title.space = 5) +
    ggside::geom_xsidedensity(fill = fillx, color = "white") +
    ggside::geom_ysidedensity(fill = fill, color = "white") +
    ggside::theme_ggside_void() +
    ggside::scale_ysidex_continuous(expand = c(0, 0)) +
    ggside::scale_xsidey_continuous(expand = c(0, 0))
}
```
```{r message=FALSE, warning=FALSE}
sr <- c("Confidence_Fake", "Confidence_Real", "n_Real")

r <- make_correlation(dfsub[sr], select(dfsub, starts_with("IPIP")))
filter(r, BF > 1)
```

@@

```{r message=FALSE, warning=FALSE}
p1 <- plot_correlation(dfsub,
  x = "IPIP6_HonestyHumility",
  y = "Confidence_Real",
  ylab = "Confidence that the stimulus is real",
  xlab = "Honesty-Humility",
  fillx = "#00BCD4",
  fill = "#D81B60"
) + 
  scale_y_continuous(labels=scales::percent)

p2 <- plot_correlation(dfsub,
  y = "Confidence_Fake",
  x = "AI_Enthusiasm",
  ylab = "Confidence that the stimulus is fake",
  xlab = "Enthusiasm about AI technology",
  fillx = "#607D8B",
  fill = "#3F51B5"
) + 
  scale_y_continuous(labels=scales::percent)

p3 <- plot_correlation(dfsub,
  y = "Confidence_Real",
  x = "AI_Enthusiasm",
  ylab = "Confidence that the stimulus is real",
  xlab = "Enthusiasm about AI technology",
  fillx = "#607D8B",
  fill = "#D81B60"
) + 
  scale_y_continuous(labels=scales::percent)

p4 <- plot_correlation(dfsub,
  y = "Confidence_Real",
  x = "FFNI_AcclaimSeeking",
  ylab = "Confidence that the stimulus is real",
  xlab = "Narcissism (Acclaim Seeking)",
  fillx = "#FF9800",
  fill = "#D81B60"
) + 
  scale_y_continuous(labels=scales::percent)

p5 <- plot_correlation(dfsub,
  y = "Confidence_Fake",
  x = "FFNI_AcclaimSeeking",
  ylab = "Confidence that the stimulus is fake",
  xlab = "Narcissism (Acclaim Seeking)",
  fillx = "#FF9800",
  fill = "#3F51B5"
) + 
  scale_y_continuous(labels=scales::percent)

p6 <- plot_correlation(dfsub,
  y = "Confidence_Real",
  x = "FFNI_GrandioseFantasies",
  ylab = "Confidence that the stimulus is real",
  xlab = "Narcissism (Grandiose Fantasies)",
  fillx = "#FFC107",
  fill = "#D81B60"
) + 
  scale_y_continuous(labels=scales::percent)

fig <- wrap_elements(fig1a) /
  wrap_elements(
    ((p3 / p2) | (p1 / p6) | (p4 / p5)) + 
  plot_annotation(title = "Personality Correlates of Simulation Monitoring Tendencies", theme = theme(plot.title = element_text(face = "bold", hjust = 0.5)))
  ) +
  plot_layout(heights = c(1.1, 0.9))

ggsave("figures/Figure2.png", width=fig.height * 1.8, height=fig.width * 1.5)
```

### 2022-09-13 submission/manuscript.Rmd
ms

<!-- Objective features -->
Technology allows already to create near-perfect simulations indistinguishable from reality. If real and fake stimuli are identical based on their objective characteristics, how can we make - hopefully accurate - judgments regarding their nature?

<!-- Context -->
Literatue shows that context surrounding stimuli plays an important role. But in the absence of context, what drives the beliefs of reality?

<!-- Internal features -->
Psychological factors. Stable dispositional traits. Reactive characteristics.

>>>>

<!-- stakes and Post-truth era -->
For the first time in Humanity's history, technology has enabled the creation of near-perfect simulations indistinguishable from reality. These artificial yet realistic constructs permeate all areas of life through immersive works of fiction, deep fakes (real-like images and videos generated by deep learning algorithms), virtual and augmented reality, artificial beings (artificial intelligence "bots" with or without a physical form), fake news and skewed narratives which ground truth is often hard to access. They carry important consequences for the technological and entertainment sector, but also for security and politics, for instance if used for propaganda and disinformation, recruitment into malevolent organizations, or religious indoctrination. This challenge is central to what has been coined as the "post-truth era" (**REF Lewandowsky et al., 2017**), in which the distinction (and lack thereof) between authentic and simulated objects will play a critical role.

<!-- Ambiguous stimuli and irrelevance of objective features -->
While there are still some fields in which simulations are not perfectly realistic (e.g., Computer Generated Images - CGI in movies often lack the details and appearance of reality), it is fair to assume that these technical limitations will become negligible in the near future. This fact, however, leads to a new issue: if real and fake stimuli cannot be distinguished based on their objective characteristics, how can we make judgments regarding their nature?

<!-- Context -->
Literature shows that context surrounding stimuli plays an important role in the assessment of its reality (a process henceforth referred to as *simulation monitoring*, **REF makowski2019phenomenal and makowski 2018 thesis**). *Blabla some literature and references on how we use the context (source of information, author of information, knowledge about credibility and things like that)*. What drives the beliefs of reality in the absence of contextual cues (**Figure 1**).

```{r message=FALSE, warning=FALSE, fig.cap="The decision to believe that an imbiguous stimulus (of any form, e.g., images, text, videos, environments, ...) is real or fake depends of individual characteristics (e.g., personality and cognitive styles), stimulus-related features (context, emotionality), and their interaction, which can manifest for instance in our bodily reaction.", out.width="100%"}
knitr::include_graphics("../figures/Figure1.png")
```

<!-- Internal features -->
Psychological factors. Stable dispositional traits. Cognitive styles and the like

<!-- Reactive features -->
Aside from stimulus- and individual-realted characteristics, it is possible that simulation monitoring is driven by the interaction between the two, i.e., by the reaction associated with the experience of a given stimulus. For instance, emotions. Lines of evidence found in the link between presence and emotion (see *makowski2017avengers* and more) and fiction and emotion regulation (fictional reappraisal papers from makowski and more). Other include familiarity and self-relevance (can cite sperduti fiction 1 here).

<!-- Attractiveness -->
Images of faces, one of the most comon artificial inteligence (AI) target, integrate components of emotional reaction, saliency, self-relevance via attractiveness (REF). Talk about possible links between attractiveness and simulation monitoring

<!-- Goals and hypotheses -->

```{r message=FALSE, warning=FALSE, fig.cap="Top part shows blabla.", out.width="100%"}
knitr::include_graphics("../figures/Figure2.png")
```

## Methods

### Procedure

### Participants

## Results

## Discussion
